---
title: "ottr sample Rmd"
author: "Chris Pyles"
date: "7/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**this assumes you have already installed ottr from the repo**

```{r}
library(datasets)
library(dplyr)
library(readr)
```

**Question 1:** Find the radius of a circle that has a 90 deg. arc of length 2. Assign this value to `ans.1`

```{r}
ans.1 <- 2 * 2 * pi * 2 / pi / pi / 2
```

```{r}
. = ottr::check("tests/q1.R")
```

**Question 2:** Load the iris dataset. Use dplyr's `filter` function to create `setosas` as the subset of `iris` containing only setosas.

```{r}
data(iris)
setosas <- iris %>% filter(Species == "setosa")
```

```{r}
. = ottr::check("tests/q2.R")
```

**Question 3:** Using the iris dataset, create two indicator variables for the iris species and then create a linear regression model regressing sepal length on sepal width and the species dummy variables.

```{r}
iris$setosa = iris$Species == "setosa"
iris$versicolor = iris$Species == "versicolor"
model = lm(Sepal.Length ~ Sepal.Width + setosa + versicolor, data=iris)
```

```{r}
. = ottr::check("tests/q3.R")
```

**Question 4:** Use dplyr to load `data/galton.csv`. Create a linear regression model of child height on father and mother height.

```{r}
galton = read_csv("data/galton.csv")
model = lm(childHeight ~ mother + father, data=galton)
```

```{r}
. = ottr::check("tests/q4.R")
```
