---
title: "Otter Assign for Rmd Sample"
author: "Chris Pyles"
output: pdf_document
---

```
BEGIN ASSIGNMENT
requirements: requirements.R
generate: true
files:
  - data
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Otter Assign for Rmd Sample Notebook

```{r}
library(datasets)
library(dplyr)
library(readr)
library(ggplot2)
```

**Question 1:** Find the radius of a circle that has a 90 deg. arc of length 2. Assign this value to `ans.1`

```
BEGIN QUESTION
name: q1
manual: false
points:
  - 1
  - 1
```

```{r}
ans.1 <- 2 * 2 * pi * 2 / pi / pi / 2 # SOLUTION
```

```{r}
## Test ##
test_that("q1a", {
  expect_true(ans.1 > 1)
  expect_true(ans.1 < 2)
})
```

```{r}
## Hidden Test ##
test_that("q1b", {
  tol = 1e-5
  actual_answer = 1.27324
  expect_true(ans.1 > actual_answer - tol)
  expect_true(ans.1 < actual_answer + tol)
})
```

**This paragraph is outside of a question.** Let's check that it appears in the output.

```{r}
# so is this code cell
```

**Question 2:** Load the iris dataset. Use dplyr's `filter` function to create `setosas` as the subset of `iris` containing only setosas.

```
BEGIN QUESTION
name: q2
points: 3
```

```{r}
data(iris)                                        # SOLUTION
setosas <- iris %>% filter(Species == "setosa")   # SOLUTION
```

```{r}
## Test ##
test_that("q2a", {
  expect_equal(nrow(iris), 150)
  expect_equal(length(names(iris)), 5)
  for (col_name in c("Sepal.Length", "Sepal.Width", "Petal.Length", "Petal.Width", "Species")) {
    expect_true(col_name %in% names(iris))
  }
})
```

```{r}
## Test ##
test_that("q2b", {
  expect_equal(nrow(setosas), 50)
  expect_equal(length(unique(setosas$Species)), 1)
})
```

```{r}
## Hidden Test ##
test_that("q2c", {
  expect_equal(length(unique(iris$Species)), 3)
  expect_equal(iris[1, "Sepal.Length"], 5.1)
})
```

**Question 3:** Using the iris dataset, create two indicator variables for the iris species and then create a linear regression model regressing sepal length on sepal width and the species dummy variables.

```
BEGIN QUESTION
name: q3
points:
  - 1
  - 1
  - 1
```

```{r}
# BEGIN SOLUTION
iris$setosa = iris$Species == "setosa"
iris$versicolor = iris$Species == "versicolor"
model = lm(Sepal.Length ~ Sepal.Width + setosa + versicolor, data=iris)
# END SOLUTION
```

```{r}
## Test ##
test_that("q3a", {
  expect_equal(length(names(iris)), 7)
  for (col_name in c("Sepal.Length", "Sepal.Width", "Petal.Length", "Petal.Width", "Species")) {
    expect_true(col_name %in% names(iris))
  }
  expect_equal(length(names(iris)[names(iris) %in% iris$Species]), 2)
})
```

```{r}
## Test ##
test_that("q3b", {
  expect_equal(length(model$coefficients), 4)
  expect_true("Sepal.Width" %in% names(model$coefficients))
  expect_true("Sepal.Length" %in% colnames(model$model))
  expect_false("Sepal.Length" %in% names(model$coefficients))
})
```

```{r}
## Hidden Test ##
test_that("q3c", {
  for (col_name in names(iris)) {
    if (!(col_name %in% c("Sepal.Length", "Sepal.Width", "Petal.Length", "Petal.Width", "Species"))) {
      expect_equal(sum(iris[, col_name]), 50)
    }
  }
  if ("setosa" %in% names(iris)) {
    setosas = iris %>% filter(setosa == 1)
    expect_equal(mean(setosas$Petal.Length), 1.462)
  }
  if ("versicolors" %in% names(iris)) {
    versicolors = iris %>% filter(versicolor == 1)
    expect_equal(mean(versicolors$Petal.Length), 4.26)
  }
})
```

**Question 4:** Use dplyr to load `data/galton.csv`. Create a linear regression model of child height on father and mother height.

```
BEGIN QUESTION
name: q4
points: 2
```

```{r}
# BEGIN SOLUTION NO PROMPT
galton = read_csv("data/galton.csv")
model = lm(childHeight ~ mother + father, data=galton)
# END SOLUTION
. = " # BEGIN PROMPT
# put your code here
...
" # END PROMPT
```

```{r}
## Test ##
test_that("q4a", {
  expect_equal(length(model$coefficients), 3)
  expect_true("father" %in% names(model$coefficients))
  expect_true("mother" %in% names(model$coefficients))
})
```

```{r}
## Hidden Test ##
test_that("q4b", {
  tol = 1e-5
  actual_values = c(22.6432797, 0.3682823, 0.2905100)
  coeffs = model$coefficients[c("(Intercept)", "father", "mother")]
  for (i in 1:3) {
    expect_true(coeffs[i] > actual_values[i] - tol)
    expect_true(coeffs[i] < actual_values[i] + tol)
  }
})
```

**Question 5:** Simplify $\sum_{i=1}^n n$.

```
BEGIN QUESTION
name: q5
manual: true
```

<!-- BEGIN SOLUTION -->
$\frac{n(n+1)}{2}$
<!-- END SOLUTION -->

**Question 6:** Fill in the blank.

```
BEGIN QUESTION
name: q6
manual: true
```

<!-- BEGIN PROMPT -->
The mitochonrida is the ___________ of the cell.
<!-- END PROMPT -->

<!-- BEGIN SOLUTION NO PROMPT -->
powerhouse
<!-- END SOLUTION -->

**Question 7:** Plot $f(x) = \cos e^x$ on $[0,10]$.

```
BEGIN QUESTION
name: q7
manual: true
```

```{r}
# BEGIN SOLUTION
x = seq(0, 10, 0.01)
y = cos(exp(x))
ggplot(data.frame(x, y), aes(x=x, y=y)) +
  geom_line()
# END SOLUTION
```
